%-------------------------
% Resume in Latex
% Author : Seif Zakaria
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Seif Zakaria} \\ \vspace{1pt}
    Full-stack Software Engineer -- Cairo, Egypt \\ \vspace{1pt}
    \small +201558173354 $|$ \href{mailto:seifzellaban@gmail.com}{\underline{seifzellaban@gmail.com}} $|$ 
    \href{https://linkedin.com/in/seifzellaban}{\underline{linkedin.com/in/seifzellaban}} $|$
    \href{https://seifzellaban.work}{\underline{Portfolio}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ain Shams University}{}
      {Bachelor’s degree in Computer Science and Statistics}{Cairo, Egypt}
    \resumeSubheading
      {DEPI x EYouth}{}
      {MERN Stack Full Stack Web Development Diploma}{Cairo, Egypt}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Algorithms Analysis
                \item Design Patterns
                \item Database Management
                \item Networking
                \item Systems Programming
                \item Web Development
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Masons}{Sept 2020 -- Present}
      {Founder \& Full-stack Software Engineer}{Cairo, Egypt}
        \resumeItemListStart
            \resumeItem{Led team through three NASA Space Apps Challenge iterations, achieving local winner status.}
            \resumeItem{Mentored team members to increase project delivery rate by 40\%.}
            \resumeItem{Expanded organization's reach and membership through improved accessibility initiatives.}
        \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{My Portfolio} $|$ \emph{Next.js, TailwindCSS, JavaScript, Framer Motion, Shadcn UI}}{January 2025}
            \resumeItemListStart
                \resumeItem{Built a responsive multi-page portfolio using Next.js with modern page transitions and animations using Motion.}
                \resumeItem{Implemented reusable UI components with Shadcn UI and TailwindCSS for consistent design.}
        \resumeItemListEnd
        \vspace{-13pt}
        \resumeProjectHeading
            {\textbf{Orbit} $|$ \emph{Next.js, Three.js, JavaScript, NASA's APIs}}{Sep. 2024 -- Oct. 2024}
            \resumeItemListStart
                \resumeItem{Developed an interactive 3D solar system simulation with real-time NEO tracking, utilizing NASA's Small Body Database using Next.js, and Three.js.}
        \resumeItemListEnd
        \vspace{-13pt}

        \resumeProjectHeading
            {\textbf{911} $|$ \emph{Python, MySQL, Workbench, PowerPoint}}{Nov. 2023 -- Dec. 2023}
            \resumeItemListStart
                \resumeItem{Developed data randomization scripts to automate and optimize data handling processes.}
                \resumeItem{Created efficient data extraction algorithm, reducing processing time by 340\% for every 50 entries.}
            \resumeItemListEnd
            \vspace{-13pt}
          
        \resumeProjectHeading
            {\textbf{NAVERIS} $|$ \emph{Python, Git, PowerPoint}}{Sep. 2023 -- Oct. 2023}
            \resumeItemListStart
                \resumeItem{Built backend integration with OpenWeather API for weather data collection.}
                \resumeItem{Implemented dotmatrix algorithm for precise geographical area mapping.}
            \resumeItemListEnd
            % \vspace{-13pt}
      
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, C++, Python, SQL (MySQL), MongoDB} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Express.js, Tailwind CSS, Bootstrap} \\
     \textbf{DevOps \& Tools}{: Linux, Git, Docker, VS Code, Visual Studio, Workbench, Microsoft Office Suite} \\
     \textbf{Soft Skills}{: HRM, Public Speaking, Team Leadership, Time Management, English Copywriting and Communication}
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership \& Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Open Source Community}{Nov. 2024 -- Present}{Head of Human Resources}{Ain Shams University}
            \resumeItemListStart
            \resumeItem{Streamlined the interviewing process, and increased interviews by 94\% in the recruitment, and conducted 37 personally.}
            \resumeItem{Authored HR guidelines covering rules, rewards, and the OSC operational framework.}
            \resumeItem{Led weekly mentorship on evaluation, KPIs, leadership, time management, and professional skills.}
            \resumeItem{Completed 20+ hours of advanced interview training, improving talent acquisition.}
            \resumeItem{Organized 2 workshops for 50+ participants, increasing engagement by 13\%.}
        \resumeItemListEnd

        \resumeSubheading{Open Source Community}{Nov. 2023 -- Present}{Public Relations Team Lead}{Ain Shams University}
            \resumeItemListStart
                \resumeItem{Delivered keynote speeches to 300+ freshmen, significantly expanding community reach.}
                \resumeItem{Executed social media campaigns driving 9\% engagement growth.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
